A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
Add tables for call counts and call sites

In our corpus eval is called \missingNumber times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. \missingTable breaks down the number of calls and callsites for
the four kinds of eval functions from the three source; core R, packages and
Kaggle code.

The core R packages are the biggest consumers of eval. Majority of calls,
\missingPercentage, originate from the core R packages. Kaggle code, which is
end-user code, has merely \missingNumber calls to eval.

>>>>

In our corpus eval is called \AllAllCallCountRnd{} times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. \missingTable breaks down the number of calls and callsites for
the four kinds of eval functions from the three source; core R, packages and
Kaggle code.

\begin{tabular}{c|c|c|c|c|c}
  Function  & Core & Packages & Kaggle & All \\
  eval & \CoreEvalCallCountRnd & \PackageEvalCallCountRnd & \KaggleEvalCallCountRnd & \AllEvalCallCountRnd \\
  evalParent & \CoreEvalParentCallCountRnd & \PackageEvalParentCallCountRnd & \KaggleEvalParentCallCountRnd & \AllEvalParentCallCountRnd \\
  evalq & \CoreEvalqCallCountRnd & \PackageEvalqCallCountRnd & \KaggleEvalqCallCountRnd & \AllEvalqCallCountRnd \\
  local & \CoreLocalCallCountRnd & \PackageLocalCallCountRnd & \KaggleLocalCallCountRnd & \AllLocalCallCountRnd \\
  all & \CoreAllCallCountRnd & \PackageAllCallCountRnd & \KaggleAllCallCountRnd & \AllAllCallCountRnd
\end{tabular}

\begin{tabular}{c|c|c|c|c|c}
  Function  & Core & Packages & Kaggle & All \\
  eval & \CoreEvalSiteCountRnd & \PackageEvalSiteCountRnd & \KaggleEvalSiteCountRnd & \AllEvalSiteCountRnd \\
  evalParent & \CoreEvalParentSiteCountRnd & \PackageEvalParentSiteCountRnd & \KaggleEvalParentSiteCountRnd & \AllEvalParentSiteCountRnd \\
  evalq & \CoreEvalqSiteCountRnd & \PackageEvalqSiteCountRnd & \KaggleEvalqSiteCountRnd & \AllEvalqSiteCountRnd \\
  local & \CoreLocalSiteCountRnd & \PackageLocalSiteCountRnd & \KaggleLocalSiteCountRnd & \AllLocalSiteCountRnd \\
  all & \CoreAllSiteCountRnd & \PackageAllSiteCountRnd & \KaggleAllSiteCountRnd & \AllAllSiteCountRnd
\end{tabular}

The core R packages are the biggest consumers of eval. Majority of calls,
\CoreAllCallCountRnd, originate from the core R packages. Kaggle code, which is
end-user code, has merely \AllKaggleCallCountRnd calls to eval.
